\Title

### 2021-12-08 latex/paper/main.tex
Updated the paper to include the new paper I found which uses VNHCs of the form h = qa - f(qu,pu)

%/========== Main Document ==========/%
\begin{document}
\title{\Title}
\author{Adan Moran-MacDonald, \IEEEmembership{Member, IEEE}, Manfredi Maggiore,
\IEEEmembership{Member, IEEE}*, and Xingbo Wang
\thanks{Manuscript submitted for review on \today.}
\thanks{A. Moran-MacDonald (e-mail: adan.moran@mail.utoronto.ca) and
M. Maggiore (e-mail: maggiore@control.utoronto.ca) are with the Department of
Electrical and Computer Engineering, University of Toronto, ON, Canada.}
\thanks{X. Wang is with ??? (e-mail: ???).}
} %/author

@@

Griffin and Grizzle \cite{nhvc_dynamic_walking} were the first to define relative degree two nonholonomic constraints which can be enforced through state feedback. Horn \etal later extended their results in \cite{hybrid_zero_dynamics_bipedal_nhvcs} to derive the constrained dynamics for a certain class of mechanical systems. These researchers made use of the unactuated conjugate momentum, but they developed their results in the Lagrangian framework. In particular, they focused on Lagrangian systems with degree of underactuation one. We will now present a special case of \cite{hybrid_zero_dynamics_bipedal_nhvcs} for simply actuated Hamiltonian systems, so that the theory we apply to the acrobot is provided in its clearest form. After we finish this summary we will clarify the relationship between our material and that of \cite{hybrid_zero_dynamics_bipedal_nhvcs}.

@@

\textbf{Comparison with existing literature}: Horn \etal provide the constrained
dynamics for \vnhcs in \cite{nhvc_incline_walking}.
Their assumption \textbf{H2} is what we call regularity, and our requirement
that one can solve for \(q_a = f(q_u,p_u)\) on \(\Gamma\) implies their
assumption \textbf{H3} holds true.
The only real distinction between this section and their work is that
our constrained dynamics are explicit functions of the Hamiltonian coordinates
\((q_u,p_u)\).
In fact, one can show that the constrained dynamics \eqref{eqn:qpu-dynamics}
coincide with the constrained dynamics in
\cite[Eqn. (17)]{hybrid_zero_dynamics_bipedal_nhvcs}
when one chooses the special case \(\theta_1 = q_u\) and 
\(\theta_2 = p_u\).
This explicit representation will be beneficial when we apply the theory of
\vnhcs to the acrobot.

>>>>

%/========== Main Document ==========/%
\begin{document}
\title{\Title}
\author{Adan Moran-MacDonald, \IEEEmembership{Member, IEEE}, Manfredi Maggiore,
\IEEEmembership{Member, IEEE}*, and Xingbo Wang
\thanks{Manuscript submitted for review on \today.}
\thanks{A. Moran-MacDonald (e-mail: adan.moran@mail.utoronto.ca),
M. Maggiore (e-mail: maggiore@control.utoronto.ca), and
X. Wang (e-mail: xingbo.wang@utoronto.ca) are with the Department of
Electrical and Computer Engineering, University of Toronto, ON, Canada.}
} %/author

@@

Griffin and Grizzle \cite{nhvc_dynamic_walking} were the first to define
relative degree two nonholonomic constraints which can be enforced through state
feedback. Horn \etal extended their results in
\cite{hybrid_zero_dynamics_bipedal_nhvcs} to derive the constrained dynamics for
a certain class of mechanical systems. 
Hamed and Ames \cite{nonholonomic_hybrid_zero_dynamics} then found an explicit
representation of these constrained dynamics for virtual
nonholonomic constraints with a specific form.
All these researchers made use of the
unactuated conjugate momentum, but they developed their results in the
Lagrangian framework. In particular, they focused on Lagrangian systems with
degree of underactuation one. We will now present a special case of
\cite{hybrid_zero_dynamics_bipedal_nhvcs} for simply actuated Hamiltonian
systems, so that the theory we apply to the acrobot is provided in its clearest
form. After we finish this summary we will clarify the relationship between our
material and that of 
\cite{hybrid_zero_dynamics_bipedal_nhvcs,nonholonomic_hybrid_zero_dynamics}.

@@

\textbf{Comparison with existing literature}: Horn \etal provide the constrained
dynamics for \vnhcs in \cite{nhvc_incline_walking}.
Their assumption \textbf{H2} is what we call regularity, and our requirement
that one can solve for \(q_a = f(q_u,p_u)\) on \(\Gamma\) implies their
assumption \textbf{H3} holds true.
Constraints of this form are used by Hamed and Ames in
\cite{nonholonomic_hybrid_zero_dynamics}.
%The only real distinction between this section and their work is that
%our constrained dynamics are explicit functions of the Hamiltonian coordinates
%\((q_u,p_u)\).
In fact, one can show that the constrained dynamics \eqref{eqn:qpu-dynamics}
are exactly the constrained dynamics in
\cite[Eqn. (9)]{nonholonomic_hybrid_zero_dynamics}, which coincide with 
\cite[Eqn. (17)]{hybrid_zero_dynamics_bipedal_nhvcs}
when one chooses the special case \(\theta_1 = q_u\) and 
\(\theta_2 = p_u\).
The only real distinction between this section and the work of
\cite{nonholonomic_hybrid_zero_dynamics,hybrid_zero_dynamics_bipedal_nhvcs} is
that our constrained dynamics are derived in the Hamiltonian framework. 
%This explicit representation will be beneficial when we apply the theory of
%\vnhcs to the acrobot.
